Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-08-30 manu-draft.qmd
addl pyro content
added nms fig but need to add caption, working gam but need to create plot and tables
added gam results figure

@@

OTB seagrass loss and role of pyrodinium, optimal temperatures from 28-31 [@lopez2021]. For salinity, highest growth rates at 24 psu and above, with decline in growth rates at 20 psu [@usup1994], in Florida growth has occurred in psu 10-45, bloom concentrations observed above 15 psu [@phlips2006; @lopez2021].

@@

>>>>

NMS results in @fig-nms and GAM results in @fig-gamres.

@@

OTB seagrass loss and role of pyrodinium, optimal temperatures from 28-31 [@lopez2021]. For salinity, highest growth rates at 24 psu and above, with decline in growth rates at 20 psu [@usup1994], in Florida growth has occurred in psu 10-45, bloom concentrations observed above 15 psu [@phlips2006; @lopez2021]. Optimal salinity range between 20-32 psu [@lopez2021].

@@

![Ordination plots of Nonmetric Multidimensional Scaling results for annual estimates in each bay segment for total seagrass frequency occurrence (Freq. Occ.), counts of days above the temperature threshold (Temp.), counts of days below the salinity threshold (Sal.), and counts of days above or below for both, respectively (Sal. + Temp.). Points are sized by seagrass frequency occurrence.  95% confidence ellipses are shown for observations in each major bay segment  OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay.](figs/nms.png){#fig-nms}

![Predicted results from a Generalized Additive Model evaluating frequency occurrence of seagrass versus year (left), number of days in a year when temperature exceeded the threshold (top right), and number of days in a year when salinity was below the threshold (bottom right).  Year was fit as a main effect, whereas the temperature and salinity counts were fit with interactions by year.  The right plots show model predicted results for the threshold variables for selected year slices.  2016 to 2022 are years with recent seagrass decline. Shaded areas are 95% confidence intervals.](figs/gamres.png){#fig-gamres}
